Parallel Simulation of Adaptive Random Boolean Networks

### 2016-07-14 Paper/paper.tex
Move 'such representation allows...' to experimental study

	 Such representation allows for experimenting with different SpMV algorithms. These algorithms mainly aim at maximizing memory throughput and data locality, thus reducing the overall GPU kernel execution time. We chose compressed sparse-row (CSR) matrix storage format and implemented an SpMV kernel as described in \cite{bell2008efficient}, as it shows the best performance on unstructured matrices.

@@

	Both algorithms were implemented using C++ programming language. The implementation is cross-platform and requires a GPU with CUDA compute capability at least 1.2.

@@

	\paragraph{Speedup obtained by GPU acceleration.} We measured the execution times of both serial and parallel versions of state updates. We used Liu-Bassler algorithm with checkpoints $T$ = $\{100,$ $200,$ $1000,$ $2000,$ $...,$ $10^7,$ $2 \cdot 10^7\}$, $\mu_{max} = 10^7$. To decrease the number of random samples required to compare the versions, we did not stop the epoch as soon as an attractor was found. Instead, we performed all $2 \cdot 10^7$ state updates per epoch. Such simulation corresponds to the worst-case scenario when no attractors were found, i. e. $R = 0\%$. The results presented in Figure \ref{fig:speedup} indicate that the GPU implementation is more efficient than the serial one for networks consisting of more than $200$ nodes.

>>>>

@@

	Both algorithms were implemented using C++ programming language. The implementation is cross-platform and requires a GPU with CUDA compute capability at least 1.2. The representation of RBNs' state update function defined in Eq. \ref{eq:spmv}, \ref{eq:gather} allows for experimenting with different SpMV algorithms. These algorithms mainly aim at maximizing memory throughput and data locality, thus reducing the overall GPU kernel execution time. We chose compressed sparse-row (CSR) matrix storage format and implemented an sparse matrix-vector multiplication kernel as described in \cite{bell2008efficient}, as it shows the best performance on unstructured matrices.

@@

	\paragraph{Speedup obtained by GPU acceleration.} We measured the execution times of both sequential and parallel versions of state updates. We used Liu-Bassler algorithm with checkpoints $T$ = $\{100,$ $200,$ $1000,$ $2000,$ $...,$ $10^7,$ $2 \cdot 10^7\}$, $\mu_{max} = 10^7$. To decrease the number of random samples required to compare the versions, we did not stop the epoch as soon as an attractor was found. Instead, we performed all $2 \cdot 10^7$ state updates per epoch. Such simulation corresponds to the worst-case scenario when no attractors were found, i. e. $R = 0\%$. The results presented in Figure \ref{fig:speedup} indicate that the GPU implementation is more efficient than the serial one for networks consisting of more than $200$ nodes.
